A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
small changes

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to promote efficient
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We evaluate our approach
in large problems from a realistic robot exploration domain.

>>>>

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to promote efficient
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small abstract subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We evaluate our approach
in large problems from a realistic robot exploration domain.

### 2011-02-08 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
small changes

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive DT planning. Given a
DTPDDL model of the environment, sequential planning is used to
compute an initial deterministic sequential plan and complementary
runtime evolution of the decision process. That plan is executed until
testing of an assumption about the runtime state is scheduled. At that
point a DT session performs some sensing which determines whether or
not the sequential session should be allowed to continue, or otherwise
acts to achieve the overall objectives. We find our approach performs
quickly and relatively efficiently in a number of large real-world
task and observation planning problems.

>>>>

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a planner that
switches between fast sequential and expensive DT planning in small
abstractions of the problem at hand. Given a DTPDDL model of the
environment, sequential planning is used to compute an initial
deterministic sequential plan and complementary runtime evolution of
the decision process. That plan is executed until testing of an
assumption about the runtime state is scheduled. At that point a DT
session performs some sensing which determines whether or not the
sequential session should be allowed to continue, or otherwise acts to
achieve the overall objectives. We find our approach performs quickly
and relatively efficiently in a number of large real-world task and
observation planning problems.
